---
title: "How to install and update `flfishltm`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{How to install and update `flfishltm`}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Installation

`flfishltm` is stored in a custom repository on r-universe.dev, not the default CRAN repository. Therefore to use the standard `install.packages()` function, you must reference the `flfishltm` repository which is located at [https://jasono6359.r-universe.dev](https://jasono6359.r-universe.dev). 

```{r eval=FALSE}
install.packages("flfishltm", repos = "https://jasono6359.r-universe.dev")
```

To ease updating the package in the future, we recommend storing a persistent reference to the repository in in your user .Rprofile. This way the repository is available every time you start a new R session. To do this first call:

```{r eval=FALSE}
usethis::edit_r_profile(scope = "user")
```

This will open your .Rprofile file. Then copy and paste the following into your .Rprofile: 

```{r eval=FALSE}
local({
  options(repos = 
            c(flfishltm = "https://jasono6359.r-universe.dev",
              CRAN = "https://cloud.r-project.org"))})

```

Then save and close .Rprofile. 

Now restart your r session, if using Rstudio you can simply hit ctrl + shift + F10. Then you can check that the repository reference has been saved by running:

```{r eval=FALSE}
install.packages("flfishltm")
```

If this runs without error then the repository reference has been set and you can update your `flfishltm` package in the future by simply rerunning this command.
